Sharing statistics for SPARQL Federation optimization, with emphasis on benchmark quality

### 2012-01-11 eswc-2012/phdsymp.tex
fed sota
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@62 43ef1190-90fd-4dd7-a769-d0121f02b80e

I take the technology state of the art to be represented by the
current basic SPARQL 1.1 Federated Query Working
Draft\footnote{http://www.w3.org/TR/2011/WD-sparql11-federated-query-20111117/}. For
an academic treatment of the current specification, see
\cite{springerlink:10.1007/978-3-642-21064-8_1} and references therein.

In \cite{springerlink:10.1007/978-3-642-21064-8_1}, the authors show
an optimization strategy based on execution order of different
algebraic elements. % TODO: wording here

In \cite{5337556}, it is shown how histograms can be computed to
assist the SemWIQ optimizer, written by the same authors.
% RDFStats

>>>>

I take the technology state of the art to be represented by the
current basic SPARQL 1.1 Federated Query Working
Draft\footnote{http://www.w3.org/TR/2011/WD-sparql11-federated-query-20111117/}.

A recent scientific treatment of the current specification, is in
\cite{springerlink:10.1007/978-3-642-21064-8_1}. In this paper, the
authors also show an optimization strategy based on execution order of
different algebraic elements. % TODO: wording here

In \cite{5337556}, it is shown how various statistics-gathering
techniques, including histograms can be computed to
assist the SemWIQ optimizer, written by the same authors.

For benchmarking federated query processing strategies,
\cite{Schmidt:2011:FBS:2063016.2063054} report the development of \emph{FedBench}.
